{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-08 documents/paper.tex
words

@@

@@

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{chunk_4}
	\caption{
		\light{
		\\
		We've got a thing\\
		that's called\\
		{\it Radar Love}\\}
		We've got a wave\\
		in the air}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
%\begin{table} 
%	\centering
%	\begin{threeparttable}
%		\caption{Safety limits from various standards}
%		\begin{tabular}{lllll}
%			\toprule
%			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
%			\midrule
%			&     \multicolumn{4}{c}{Spanning text}     \\
%			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
%			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
%			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
%			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
%			\bottomrule
%		\end{tabular}
%		\begin{tablenotes}
%			\small
%			\item This is where authors provide additional information about
%			the data, including whatever notes are needed.
%		\end{tablenotes}
%	\end{threeparttable}
%\end{table}

All pertinent restrictions for frequency $<$ 6 GHz, for general public.
ICNIRP 2020, Table 2, "Basic restrictions for electromagnetic field exposure",
20 \Wsqm, averaged over a 6 min period, averaged over a square $4 \text{cm}^2$ surface area of the body.

Whole-body average SAR $<$ 0.08 W/kg

And, additionally,

ICNIRP 2020, Table 3, Basic Restrictions

\clearpage
{\Large \it The contenders}\\

\paragraph{Time-domain modulation}

However, there is an obvious avenue of optimization. If the virus is destroyed in a few dozen nanoseconds via an electric field amplitude incidentally caused by an instantaneous power $\text{P}$, but tissue damage requires a temperature rise due to an energy deposition $\text{P} \  \text{dt}$, then we should minimize dt.\

We thus turn the CW microwave signal into a series of effectively instantaneous pulses.

Note that contrary to the limits at lower frequencies, neither ICNIRP nor IEEE appear to explicitly specify a maximum electric field; only the maximum power is specified (thereby implicitly restricting the electric field magnitude).

The safety standards of [IEEE] and [ICNIRP] account for such time-domain modulation by specifying both an average power limit over a 6 minute period, and a time-integrated energy deposition limit. All known non-thermal and thermal physiological effects, including changes in the permeability of membranes, direct nerve stimulation, etc, are accounted for by obeying those two limits.

To drive home this point, apparently the best-quality evidence available fulfills sham requirements provide in-vitro. They expose blood lymphocytes to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, a whopping pulse power density of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100 $\text{W/m}^2$ (the safety limit), for 2 hours, finding no change in any of the measured quantities.

Similarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due to the temperature rise.

So it appears that this is not merely rules-lawyering to exploit a loophole in the regulations; it is a physically-informed effect.

\begin{autem}

These papers (the best quality we are aware of) were extensively cherry-picked from the literature based on the results of a meta-analysis [Vj. 2019], listing the requirements for reliable in-vitro RF experiments.\\

There are a substantial number of papers in the literature which show positive effect sizes; a select few of these are listed in the bibliography. \\

The literature reviews conducted by standards organizations.\\

We are not aware of any past uses of these microwave en-masse. We do not have the

Moreover, 
\begin{quote}

In the absence of publication bias, since the sampling error is random, all studies will be distributed symmetrically around the mean d value.

\end{quote}

\end{autem}

\clearpage
%\printbibliography[heading=none, title={}, keyword={Flagship}]
\printbibliography[heading=none, title={}, keyword={standards}]

\clearpage
{\Large \it Time-dependence}\\

The fact that the viral inactivation is non-thermal

Both [Yang 2015] and [Hung 2014] use an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision, given the focus of their paper.

The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must establish the required duration of exposure.

{\color{red} speculative hypothesizing \{ }

In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.

As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor. Yang et al. state the Q of Inf. A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME

[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture. Such a mechanism could perhaps extend the exposure required to break the capsid or membrane. Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify properties before the envelope fractures.

{\color{red}  \} }

\subfile{safety}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large Modes of application}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Sensing}

There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].

However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.

Havelka \cite{Highfrequency2011} discuss microtubules.

With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.

However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:

$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$

which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.

% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W

\end{multicols}

{\color{red} speculation \} }

>>>>

\section{Figures which have nothing to do with our conclusion but are pretty nonetheless}

@@

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{bronch_9GHz_500W_2_transparent.png}
	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{CPWG_sim_pretty_2}
	\caption{FDTD simulation geometry of the 0.3 mm coplanar waveguide exposure cell. Red object is the fluid channel. Visualized with Paraview.
		\ghfile{covidinator/electronics/simple_fdtd/run/microfluidic_coplanar.py}}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includesvg[width=\textwidth]{compChargePlot}
	\caption{
		\light{
			\\
			We've got a thing\\
			that's called\\
			{\it Radar Love}\\}
		We've got a wave\\
		in the air}
\end{figure}

@@

%\subfile{safety}

### 2021-02-08 documents/pulse_generator.tex
words

>>>>

Impedance matching to appears to be a solved problem. \cite{Microchamber2011} provide a good review, and offer a design using a high-impedance exposure cell in parallel with a 50 ohm resistor, which offers excellent performance to at least 1 GHz. Attenuator for diagnostics are also built in.

Almost   Diagnostics of such pulses are difficult.

 Attenuators with such high peak powers are difficult to obtain.

\cite{Characterization2012}

### 2021-02-08 documents/scan_converter.tex
words

We would like real-time rather than equivalent-time sampling,

@@

A digital oscilloscope capable of real-time sampling such a transient is no small feat, and it was deemed unlikely that we would be 
able to obtain access, There is also the concern that, when working with a system producing kilovolt 
pulses and an input of 5v, some harm might come to a machine worth more than the experimenter.

@@

$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F)/2} $$

where \tau is the transit time of the electron through the deflection region

>>>>

%!TeX root = scan_converter
\documentclass[paper.tex]{subfiles}
\begin{document}

\begin{autem}
This is an example of how the course of action can be distorted by engineering. In a non-pandemic scenario such a diversion might have been a reasonable. Indefensible. I am consoled that it did not account for more than 2 to 3 weeks of work.
\end{autem}

\begin{autem}
	This section is deliberately kept vague and without reference to construction details to avoid export restrictions. In any case, it is hard to imagine a technique fully developed and published in the 1940s would be of great secrecy now. 
\end{autem}

Because of the small sizes of viruses, all interesting time-domain spectroscopy results require resolving signals with greater than 10 GHz bandwidth.

So called "equivalent-time" or "sampling" oscilloscopes are less expensive; but it was hoped that it would be possible to resolve the breaking of the capsid - a transient, single-shot phenomenon -   A digital oscilloscope capable of real-time sampling such a transient is a tall order, and it did not appear that an undergraduate would be allowed access.

There is also the concern that, when measuring a system producing kilovolt pulses using an instrument with an extremely electrically delicate 1V maximum input, some harm might come to a machine worth more than the experimenter.

This turned out to be not unfounded - the kilovolt pulser used was observed to cause the RPi controlling the experiment to

However, transient recordings of sub-nanosecond phenomena were made as early as 1938 by Manfred Von Ardenne using a "micro-oscillograph". By 1946, such oscillographs - now with bandwidths in excess of 10 GHz - were readily available commercially\cite{3beam1946}, and by 1949 found extensive use for quantitative measurements of ultrafast phenomena by Fletcher\cite{Production1949} and others.

"Direct access" tubes to the logical conclusion. The design of Fletcher puts the cathode ray deflection plates essentially inside the.

The main practical limitations on oscilloscope sweep speed are discussed by Mackay\cite{New1948}, and are imposed by the Y axis deflection plate electron transit time and bandwidth (the X-axis speed is of less importance), and the beam current and sensitivity of the phosphor (faster sweeps reduce the electron flux and brightness of the dot).

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\centering
	\subfloat[Damage to the sensor, believed to be due to. ]{
	\includegraphics[width=0.3\textwidth]{e_beam_damage_2}

}
	\hfill
	\subfloat[]{
		\includegraphics[width=0.3\textwidth]{e_beam_damage}

	}
		\hfill

	\subfloat[Direct electron beam detection]{
	\includegraphics[width=0.3\textwidth]{direct_electron_beam}
}
	\caption{Second.}
		\hfill

\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering

	\caption{}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering

	\caption{}
\end{figure}

The very high voltage actually makes this much easier

means that low-sensitivity diagnostics, like lithium niobate optical probes. Not having a suitable optical bench, an electron-beam probe, similar to a streak camera, itself similar in principle to scan-conversion digitizer tubes in Tek SCD and 7912 series transient digitizers.

If a low voltage sensitivity is required, and because modern high-pixel-density CMOS sensors allow the required deflection (and therefore the entire structure) to be minimized, these are simple to design and inexpensive (much of the complexity is in the slow-wave or travelling-wave structure which is usually required to match the signal velocity to the - slowing down light without affecting its properties or drawing power is an extremely difficult problem) and can offer sample rates in the terasamples/s and analog bandwidths of many dozens of GHz, albeit with very low vertical resolution.

original von Ardenne

\begin{fquote}[Livermore Operations][\cite{Scan2008}]
An internal CCD recorder would provide high sensitivity to the swept electron beam, but a CCD in a sealed vacuum tube has never been attempted or demonstrated in the phototube facility at Livermore Operations (LO). A prototype tube would most likely be built with a phosphor screen.
\end{fquote}

@@

@@

$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F \tau)/2} $$

where $\tau$ is the transit time of the electron through the deflection region

Image intensifier microchannel plates where angled holes cause secondary electron

\end{document}

### 2021-02-08 documents/supplemental.tex
words

>>>>

\section{Sensing}

There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].

However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.

Havelka \cite{Highfrequency2011} discuss microtubules.

With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.

However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:

$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$

which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.

% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W
